---
title: "Lab 9 Intro"
date: "`r Sys.Date()`"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library("jpeg")
```

## Seating
1. If you already have a group, it will be helpful to start sitting next to each other.  
2. If you have already settled on a group, please have one member send Bry (brymoore@ucdavis.edu) an email with the names of the group members.
3. If you don't have a group, hang tight we are working on it.  
4. Please setup your computer as normal for today.  

## Warm-up
1. In the data folder there is an epidemiology data set on an outbreak of malaria.  
```{r}
malaria <- read.csv("../lab10/data/malaria.csv") %>%  clean_names()
```

2. `rdt` refers to rapid diagnostic test and they are identified here by age group.  
```{r}
head(malaria)
```

### not tidy because title names include data 
3. Make the data tidy and store them as a new object. 
```{r}
malaria %>% 
filter(data_date == "2020-07-30") %>% 
  group_by(district) %>% 
  summarise(tot_cases=sum(cases, na.rm = T)) %>% 
  arrange(-tot_cases)
```

4. Which district had the highest *total* number of cases on July 30, 2020?  