---
title: "Lab 3 Homework"
author: "Ryan Chiang"
date: "`r Sys.Date()`"
output:
  html_document: 
    theme: spacelab
    keep_md: true
---

## Instructions
Answer the following questions and complete the exercises in RMarkdown. Please embed all of your code and push your final work to your repository. Your final lab report should be organized, clean, and run free from errors. Remember, you must remove the `#` for the included code chunks to run. Be sure to add your name to the author header above.  

Make sure to use the formatting conventions of RMarkdown to make your report neat and clean!  

## Load the tidyverse
```{r message=FALSE, warning=FALSE}
library(tidyverse)
```

### Mammals Sleep  
1. For this assignment, we are going to use built-in data on mammal sleep patterns. From which publication are these data taken from? Since the data are built-in you can use the help function in R. The name of the data is `msleep`.  
```{r}
msleep <- msleep
msleep
```
### This data was taken from " V. M. Savage and G. B. West. A quantitative, theoretical framework for understanding mammalian sleep. Proceedings of the National Academy of Sciences, 104 (3):1051-1056, 2007." 
2. Store these data into a new data frame `sleep`.  
```{r}
data.frame(msleep)
sleep <- data.frame(msleep)
```

3. What are the dimensions of this data frame (variables and observations)? How do you know? Please show the *code* that you used to determine this below.  
```{r}
dim(sleep)
```
### The dimensions of this data frame are 83 by 11, 83 variables and 11 observations
4. Are there any NAs in the data? How did you determine this? Please show your code.  
```{r}
glimpse(sleep)
```
### Yes there are NAs in the data, I determined this by running glimpse on the data and it showed the data, and I could easily point out where there were NAs
5. Show a list of the column names is this data frame.
```{r}
colnames(sleep)
```
###colnames gives us the names of columns
6. How many herbivores are represented in the data?  
```{r}
table(sleep$vore)
```
### there are 32 herivores in the data, I found this by running a table on the data 'sleep' specifically on the vore column
7. We are interested in two groups; small and large mammals. Let's define small as less than or equal to 19kg body weight and large as greater than or equal to 200kg body weight. Make two new dataframes (large and small) based on these parameters.
```{r}
small_mammals <- filter(sleep, bodywt<=19)
large_mammals <- filter(sleep, bodywt>=200)
data.frame(small_mammals)
data.frame(large_mammals)
```
### I used made 2 new sets of data by filter to get only mammals under 19 and over 200 then made a dataframe using the data
8. What is the mean weight for both the small and large mammals?
```{r}
mean(small_mammals$bodywt)
```

```{r}
mean(large_mammals$bodywt)
```
### the mean body weight for small mammals is 1.797847, the mean body weight for large animals is 1747.071. I did this by running mean on each set of data specifying with $ what I wanted to be averaged.
9. Using a similar approach as above, do large or small animals sleep longer on average?  
```{r}
mean(large_mammals$sleep_total)
mean(small_mammals$sleep_total)
```

### On average small mammals sleep longer than large mammals, I found this by running the mean again on each set of data but this time using $ to specify sleep_total as the column I wanted averaged.

10. Which animal is the sleepiest among the entire dataframe?
```{r}
order(sleep$sleep_total, na.last=TRUE, decreasing = TRUE)
name_of_sleepiest_animial <- (sleep[43,])
name_of_sleepiest_animial
```
# I used the order function to rank the sleepiness of each animal and it told me the row number of the sleepiest animal, I then just had to look for the row (43) and name it to show me that the Little Brown Bat is the sleepiest animal


## Push your final code to GitHub!
Please be sure that you check the `keep md` file in the knit preferences.   