---
title: "bis15lmidterm"
author: "Ryan Chiang"
date: "2024-02-03"
output: html_document
---

```{r}
library(tidyverse)
library(janitor)
library(skimr)
```

```{r}
fish <- readr::read_csv("data/Gaeta_etal_CLC_data.csv")
```

```{r}
name <- clean_names(name)
```

To find out what type of data you are working with, use the `class()` function. This is important because sometimes we will need to change the type of data to perform certain analyses.
```{r}
class(my_numeric)
class (my_integer)
```

```{r}
my_numeric <- 42
my_integer <- 2L #adding an L automatically denotes an integer
my_character <- "universe"
my_logical <- FALSE
my_complex <- 2+4i
```

You can use the `is()` and `as()` functions to clarify or specify a type of data.
```{r}
is.integer(my_numeric) #is my_numeric an integer?
```

```{r}
my_integer <- 
  as.integer(my_numeric) #create a new object specified as an integer
```

```{r}
is.integer(my_integer) #is my_numeric an integer?
```

#remove NAs from data
na.rm=T 

```{r}
fisheries$country <- as_factor(fisheries$country)
fisheries$fao_major_fishing_area <- as_factor(fisheries$fao_major_fishing_area)  
fisheries$isscaap_group_number <- as_factor(fisheries$isscaap_group_number)
fisheries$asfis_species_number <- as_factor(fisheries$asfis_species_number) 
```
### ^ clunky way to change column class



```{r}
fisheries %>% 
  select(country,isscaap_group_number, asfis_species_number, asfis_species_name, contains("1"))
```
### ^ when using select you can use contains() or starts_with/ends_with() to narrow
